---
title: "Datafest 2024"
author: "Golden Pash"
format: revealjs
---

```{r setup, cache = TRUE}
library(tidyverse)
setwd("C:/Users/sailo/Documents/University/Datafest/drive-download-20240419T003834Z-001/full_03_04")
responses <- read_csv("responses.csv")
```

## Executive summary (update pls)

- Something goes here

## Looking at grades throughout book

- Grades decrease throughout the book overtime

```{r boxplot_of_eoc_by_chapter}

```

## Do students realise what they fail to learn?

- Hannah's boxplot graph of survey results for each chapter
  - Remains consistent;y positive for all chapters
- But the boxplot graph of EOC shows decreasing results towards the later chapters

## Review question performance

- Review questions are done at the end of each chapter
- We hypothesised that they would be done better then the non-review questions (which are when the students have only just learnt the content).
```{r review_graph}
responses %>%
  select(points_earned, points_possible, review_flag, chapter_number) %>% 
  group_by(review_flag, chapter_number) %>% 
  summarise(average_points = sum(points_earned, na.rm = TRUE)/sum(points_possible, na.rm = TRUE)) %>% 
  filter(chapter_number<=9) %>% 
  pivot_wider(names_from = review_flag, values_from = average_points) %>% 
  mutate(difference = `TRUE` - `FALSE`) %>% 
  select(chapter_number, difference) %>% 
  ggplot() +
  geom_col(aes(x = chapter_number, y = difference)) +
  theme_bw() +
  scale_x_continuous(breaks = seq(min(responses$chapter_number, na.rm = TRUE), max(responses$chapter_number, na.rm = TRUE), by = 1)) +
  labs(x = "Chapter number", y = "Increase in score in review questions (%)")
```

## Trying to expain poor review performance

- Do students spend less time on the later review pages trying to speed through it?

## 
