---
title: "Datafest 2024"
author: "Golden Pash"
format: revealjs
---

```{r setup, cache = TRUE}
library(tidyverse)
library(ggpmisc)
setwd("C:/Users/sailo/Documents/University/Datafest/drive-download-20240419T003834Z-001/full_03_04")
responses <- read_csv("responses.csv")
views_eoc <- read_csv("page_views.csv")
checkpoints_eoc <- read_csv("checkpoints_eoc.csv")
```

## Executive summary (update pls)

- Something goes here

## Looking at grades throughout book

- Grades decrease throughout the book chapters

```{r boxplot_of_eoc_by_chapter}
checkpoints_eoc %>%
  ggplot(aes(x=reorder(as.character(chapter_number), as.numeric(chapter_number)), y=EOC)) +
  geom_boxplot() +
  labs(title = "EOC statistics by chapter", x="chapter", y="EOC") +
  scale_x_discrete()
```

- This is true not just for the interquartile range of students but also the top and bottom 1%
  - It is not just the low end of students dragging down the statistics
  
```{r eoc_percentiles}
# Sort the data by EOC
sorted_data <- checkpoints_eoc %>% 
  filter(chapter_number == 1) %>% 
  arrange(EOC)

# Calculate indices for percentiles
bottom_index <- round(0.01 * nrow(sorted_data))
top_index <- round(0.99 * nrow(sorted_data))
median_index <- round(0.5 * nrow(sorted_data))

# Extract student_ids for each percentile
bottom_decile <- sorted_data %>% 
  slice(1:bottom_index) %>%
  pull(student_id)

top_decile <- sorted_data %>% 
  slice((top_index + 1):nrow(sorted_data)) %>%
  pull(student_id)

median_decile <- sorted_data %>% 
  slice(round(0.495 * nrow(sorted_data)):round(0.505 * nrow(sorted_data))) %>%
  pull(student_id)

# Create the percentile column
checkpoints_eoc <- checkpoints_eoc %>% 
  mutate(percentile = case_when(
    student_id %in% bottom_decile ~ "bottom",
    student_id %in% top_decile ~ "top",
    student_id %in% median_decile ~ "middle",
    TRUE ~ NA_character_
  )) 
checkpoints_eoc$percentile <- factor(checkpoints_eoc$percentile, levels = c("top", "middle", "bottom"))

# Plotting
checkpoints_eoc %>% 
  filter(!is.na(percentile)) %>% 
  group_by(chapter_number, percentile) %>% 
  summarise(average_eoc = mean(EOC, na.rm = TRUE)) %>% 
  ungroup() %>% 
  ggplot() +
  geom_line(aes(x = chapter_number, y = average_eoc, colour = percentile, linetype = percentile)) +
  scale_colour_manual(values = c("top" = "blue", "bottom" = "red", "middle" = "black")) +
  scale_linetype_manual(values = c("top" = "solid", "bottom" = "solid", "middle" = "dashed")) +
  guides(colour = guide_legend(override.aes = list(title = "Percentile")))
```

- We additionally see that chapter 11 has an abnormal dip in grade
  - Abnormal dip = below the trend of decreasing grade as students progress to later (harder) chapters
  
## Time spent on each chapter

```{r median_engaged}
views_eoc <- inner_join(page_views,checkpoints_eoc,by=c("student_id", "chapter_number", "book")) %>% 
  select(book,chapter_number,section_number,engaged,off_page_brief, student_id,EOC) %>% 
  filter(book=="College / Statistics and Data Science (ABC)") 
  
average_eoc <- stats::aggregate(EOC~chapter_number,views_eoc,median) #average EOC

average_engage <- stats::aggregate(engaged~chapter_number,views_eoc,median)

ggplot() +
  geom_col(data = average_engage, mapping = aes(x = as.factor(chapter_number), 
                                             y=engaged),
           colour="black",fill="lightblue",alpha=0.7)+
  geom_line(data = average_eoc, mapping = aes(x=chapter_number, y=EOC*200000),
            colour="blue")+
  labs(y="Median EOC")+
  scale_y_continuous(
    name="Median Engagement (milliseconds)",
    sec.axis=sec_axis(~.*(1/200000),name="Median EOC"))+
  labs(x="Chapter Number",title="Engagement vs EOC for College/Statistics and Data Science (ABC)")

```

## Do students realise what they fail to learn?

- Hannah's boxplot graph of survey results for each chapter
  - Remains consistent;y positive for all chapters
- But the boxplot graph of EOC shows decreasing results towards the later chapters

## Review question performance

- Review questions are done at the end of each chapter
- We hypothesised that they would be done better then the non-review questions (which are when the students have only just learnt the content).
```{r review_graph}
responses %>%
  select(points_earned, points_possible, review_flag, chapter_number) %>% 
  group_by(review_flag, chapter_number) %>% 
  summarise(average_points = sum(points_earned, na.rm = TRUE)/sum(points_possible, na.rm = TRUE)) %>%
  filter(chapter_number<=9) %>% 
  pivot_wider(names_from = review_flag, values_from = average_points) %>% 
  mutate(difference = `TRUE` - `FALSE`) %>% 
  select(chapter_number, difference) %>% 
  ggplot() +
  geom_col(aes(x = chapter_number, y = difference)) +
  theme_bw() +
  scale_x_continuous(breaks = seq(min(responses$chapter_number, na.rm = TRUE), max(responses$chapter_number, na.rm = TRUE), by = 1)) +
  labs(x = "Chapter number", y = "Increase in score in review questions (%)")
```

## Trying to expain poor review performance

- Do students spend less time on the later review pages trying to speed through it?

```{r heatmap_by_review_or_not_page}
# will show if they start spending way less time on the review
```


## Performance by question type

```{r question_type_avg_points}

```
